\documentclass[a4paper,10pt]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{fontspec}
\usepackage[english]{babel}
\babelprovide[import]{english}

% Set default/Latin font to Sans Serif (Noto Sans)
\babelfont{rm}{Noto Sans}

% Load necessary packages
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

% Formatting Sections
\titleformat{\section}{\Large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% Formatting Lists
\setlist[itemize]{left=0pt, label=--, noitemsep, topsep=2pt, itemsep=1pt}

% Colors for Links
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}

\begin{document}

%--- HEADER ---
\begin{center}
    {\huge \textbf{Mateusz Kasprzak}} \\[6pt]
    \href{mailto:mateuszkasprzak8@gmail.com}{mateuszkasprzak8@gmail.com} \quad|\quad 
    +48 517 605 300 \quad|\quad 
    \href{https://github.com/matikasp}{github.com/matikasp} \quad|\quad 
    \href{https://linkedin.com/in/mmkasprzak}{linkedin.com/in/mmkasprzak}
\end{center}

\vspace{10pt}

%--- EDUCATION ---
\section{Education}
\noindent
\textbf{University of Warsaw} \hfill Warsaw, Poland \\
\textit{B.Sc. in Computer Science} \hfill Oct 2023 -- Present
\begin{itemize}
    \item Currently in my 3rd year.
    \item Focus on Algorithms, Systems, and Theoretical Computer Science.
\end{itemize}

%--- RESEARCH EXPERIENCE ---
\section{Research Experience}
\noindent
\textbf{Abstract Algebra Benchmark for LLMs} \hfill \textit{B.Sc. Thesis} \\
\textit{Research Collaboration with Google DeepMind, MIT, and University of Toronto} \hfill Oct 2025 -- Present
\begin{itemize}
    \item Collaborating with researchers to develop a rigorous mathematical benchmark for Large Language Models.
    \item Aiming to advance the capabilities of AI systems in genuine scientific discovery and formal reasoning.
    \item Focus on abstract algebra and formal verification within AI contexts.
\end{itemize}

%--- EXPERIENCE ---
\section{Experience}
\noindent
\textbf{Kalepa} \hfill Remote / Warsaw \\
\textit{Backend Software Engineering Intern} \hfill Jul 2025 -- Sep 2025
\begin{itemize}
    \item Engineered automation and data-processing pipelines for an insurance-tech startup involving unstructured data.
    \item Developed and optimized internal tools to support large-scale information handling and analysis.
    \item Utilized Python and cloud infrastructure (AWS) to enhance backend system reliability.
\end{itemize}

%--- PROJECTS ---
\section{Selected Projects}

\noindent
\textbf{High-Performance Concurrent Solver} \textit{-- C} \hfill \textit{Concurrent Programming}
\begin{itemize}
    \item Developed a highly optimized solution for a complex algorithmic problem, utilizing low-level memory management to minimize synchronization overhead.
    \item Achieved near-linear scalability with thread count while maintaining performance parity with the sequential baseline on single-thread execution.
    \item Ranked among the top solutions in the cohort for execution speed and efficiency.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Boolean Evaluator} \textit{-- Java} \hfill \textit{Concurrent Programming}
\begin{itemize}
    \item Designed a thread-safe Boolean-expression parser and evaluator supporting high-throughput batch processing.
    \item Implemented rigorous unit testing and ensured concurrency safety using mutexes and atomic operations.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{NAND Logic Simulator} \textit{-- C} \hfill \textit{Computer Architecture}
\begin{itemize}
    \item Built a low-level logic simulator to model combinational circuits starting from NAND gates.
    \item Verified complex truth tables and circuit designs, demonstrating deep understanding of digital logic.
\end{itemize}

\vspace{4pt}
\noindent
\small\textit{Full project portfolio available at:} \href{https://github.com/matikasp/University_Projects}{github.com/matikasp/University\_Projects}

%--- SKILLS ---
\section{Skills}
\begin{itemize}
    \item \textbf{Programming:} C, C++, Java, Python, NASM x86 Assembly.
    \item \textbf{Tools \& Cloud:} Git, Linux, AWS, Flask, OpenAI API.
    \item \textbf{Core Concepts:} Algorithms \& Data Structures, OS, Concurrency, Computer Architecture, Automata Theory.
    \item \textbf{Languages:} Polish (Native), English (Advanced/C1).
\end{itemize}

\end{document}